\documentclass[11pt]{report}
\usepackage{amsfonts,amssymb,amsmath,amsthm,epsfig,euscript,verbatim,graphicx, pdfpages}
\usepackage[blocks]{authblk}% The option is for block layout
\setlength{\textwidth}{6.3in}
\setlength{\textheight}{8.7in}
\setlength{\topmargin}{0pt}
\setlength{\headsep}{0pt}
\setlength{\headheight}{0pt}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}{Conjecture}


\title{The District Company \\ Status Report: 1}

\author{
Megan Mortensen\\
\small \texttt{mortensenm0704@my.uwstout.edu}
\and
Connor Phu\\
\small \texttt{phuk0784.my.uwstout.edu}
\and
Brian Dassow\\
\small \texttt{dassowb0941@my.uwstout.edu}
\and
Bella Nordahl\\
\small \texttt{nordahli0985@my.uwstout.edu}
\and
Advisor: Keith Wojciechowski\\
\small \texttt{wojciechowskik@uwstout.edu}\\
\bigskip
AMCS Program\\
University of Wisconsin, Stout
}

\date{\small Submitted: 2/4/16;  Accepted: 2/4/16;}

\begin{document}
\maketitle

\section*{\hspace{-.5cm} Team Structure}

\subsection*{\hspace{-.5cm} Team Name}
Mathematicians in District

\subsection*{\hspace{-.5cm} Job Titles}
Developvers: Brian, Connor, Megan, and Bella
\newline
Modelers: Brian, Connor, Megan, and Bella
\newline
Coordinator: Bella

\section*{\hspace{-.5cm} Problem Statement}\label{intro}
The problem presented by The District Company is to use data analytics to inform
their marketing strategies.

\subsection*{\hspace{-.5cm} What does the Company Do?}\label{overview}
The District Company provides a unique environment for gamers of all ages in a
social setting.  They focus on all types of games including board games, card
games, or console games in a competitive or friendly manner.


\subsection*{\hspace{-.5cm} What is the Problem?}\label{tech}
The District Company has given us the problem to inform them about best
marketing strategies for their specific events.  They would like to use these
marketing strategies to figure out which customers would be best geared for
their certain events, therefore getting a maximum return.

\subsection*{\hspace{-.5cm} Why is the Problem Important to the
Client?}\label{tech} This is an important problem to the company because if the data is used
correctly to find good marketing strategies for each set of customers, The
District Company will get a maximum return and a higher profit.

\subsection*{\hspace{-.5cm} What are the Expectations?}\label{tech}
We believe that the company would like to see some models of a linear regression
showing what marketing strategies would be best for them.  We believe they would
also like to see a report on our findings.


\end{document}
